%! Author = Stepan and Sean
%! Date = 2019-07-20

% Preamble
\documentclass[11pt]{article}

% Packages
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}

\urlstyle{same}

% Document
\begin{document}

    \title{2019 Canadian election tweets \\
    OSEMN methodology \\
    Step 1: Obtain data \\
    Description of data sources to be used in this project}

    \maketitle

    \begin{abstract}
        The following document presents different data sources to be used in this project.
    \end{abstract}

    \section{Streamed twitter data} \label{sec:streamed_twitter_data}

    The main dataset that was used for this project has been produced by streaming tweets filtered by hashtags relevant to 2019 Canadian Federal elections.
    Tweets with these hashtags have been streamed continuously (with a couple of minor interruptions) from September 3rd 2019 to %TODO add finish date

    \subsection{Criteria for selecting hashtags} \label{subsec:hashtag_selection_criteria}

    The following criteria has been used for hashtag selection:

    Initial Selection:

    - Google Search: Canadian Election Hashtags.
    Source1:\url{http://politwitter.ca/page/canadian-politics-hash-tags}
    Source2: \url{http://www.davidakin.com/politicaltwits/hashtags.htm}

    - For each major political party (one that holds >0 seats in parliament), each leader was searched for on Twitter.
    Their name was turned into a hashtags.
    A brief scroll through the top tweets was done.
    Any slogan like hashtag, or common hashtags that came up were added to the list.

    - Twitter handles for political figures were also added.

    Source: https://en.wikipedia.org/wiki/List_of_federal_political_parties_in_Canada

    - Scandals were searched for the election.
    SNC-Lavalin scandal was searched, and tags mined.
    Brownface hashtag has been added for Justin Trudeau.

    Source:https://en.wikipedia.org/wiki/List_of_political_scandals_in_Canada

    Tags related to events outside of canada (US/Global Politics) were avoided.
    US Politics were especially avoided, as the number of tweets regarding US matters can easily overwhelm our dataset (the #Trump tag alone will generate more tweets than our entire list of tags).

    \subsection{List of hashtags used to filter streamed tweets} \label{subsec:list_of_hashtags}

    #canadaelection2019 #cdnpoli #ptlib #ipc #ndp #cdnleft #cpc #roft #elxn43 #canlab #polcan #polqc #PPC2019 #pttory #ptndp #ptgreen
    #ptbloc #gpc #canpoli #cdnsen #cpac #goc #lavscam #Trudeau #TrudeauMustGo #StopScheer #InItForYou #GPC #Election2019 #LetMaxin
    #LetMaxSpeek #NotAsAdvertised #LavScam #SNCLavalin #SheerHypocrisy #ScheerHypocrisy #BrownFaceTrudeau #IStandWithTrudeau
    @yfblanchet @AndrewScheer @theJagmeetSingh @MaximeBernier @JustinTrudeau @ElizabethMay

    \section{Sentiment 140} \label{sec:sentiment_140}

    In order to train a classifier, supervised learning usually requires labelled training data.
    In case of Twitter data, due to a large range of topics being discussed on 
    Sentiment 140 is a dataset

\end{document}

